---
title: "gobyPreservation"
date: "Sept 2, 2020"
output:
  md_document: default
html_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## gobyPreservation  
gobyPreservation is a research compendium that brings together the data and analyses associated with Lorencen et al. (in review), Geometric Morphometric Analysis Quantifies Nonlinear Temporal Effects of Ethanol Preservation on Round Goby Neogobius melanostomus Anatomical Traits. R scripts are provided in analysis/, human-readable data in extData/, and R-readable data in an .rda file in data/. 

Note: All analyses originally conducted and package built using R version 4.0.0 in Windows 10

### To get started using the package

```{r eval=FALSE}
options(repos=structure(c(CRAN="http://cran.r-project.org")))
install.packages("devtools")
library(devtools)
install_github("jaredhomola/gobyPreservation")
```


### Contact
Bailey M. Lorencen  
baileylorencen@gmail.com  
  
Jared J. Homola  
jaredhomola20@gmail.com  
www.jaredhomola.com  


#### Copyright (c) 2020 The Authors

Permission is hereby granted, free of charge, to any person obtaining a copy of this software and associated documentation files (the "Software"), to deal in the Software without restriction, including without limitation the rights to use, copy, modify, merge, publish, distribute, sublicense, and/or sell copies of the Software, and to permit persons to whom the Software is furnished to do so, subject to the following conditions:

The above copyright notice and this permission notice shall be included in all copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.
